Pipit: Reactive Systems in \fstar ~(Extended Abstract)

### 2023-05-03 2023pipit/Main.tex
remove prim ty
intro notes

We are interested in verifying an antilock braking system for a motorcycle\cite{huang2010design}.

>>>>

We are interested in verifying an antilock braking system for a motorcycle\cite{huang2010design}.
Antilock brakes are designed to stop wheels from locking up in emergency braking events.
Antilock braking controllers generally work by computing the \emph{wheel slip} for the wheels, which is a ratio of the wheel's rotational speed compared to the vehicle's speed.
To compute the wheel slip, then, the controller must first estimate the vehicle's speed.

\begin{itemize}
  \item example: abs / vehicle speed estimate
  \item $\blacklozenge_{t} (v_F \approx_{\epsilon} v_R) \implies \lfloor \hat{v}' \rfloor \approx_{t\epsilon} \lceil \hat{v}' \rceil$
\end{itemize}
